### 2019-02-25 Seneca.tex
chandras pass

To facilitate model optimization on serverless architecture, we have developed Seneca, 
a framework for tuning the hyperparameters for machine learning applications 
in AWS Lambda. 
The Seneca pipeline consists of packaging, deployment, serverless 
function optimization, and hyperparameter tuning. Figure~\ref{fig:seneca} 
shows the architecture of Seneca.  In the the upper-right-front, we
show the three inputs that Seneca expects from its users: a hyperparameter
configuration file, a dataset URL, and the path to 
the machine learning application.
The configuration file
specifies the range of values for each hyperparameter that the 
application expects.  Seneca uses this configuration to construct
the hyperparameter search space.  The dataset URL is a link to a
valid dataset stored in S3.

Seneca automatically builds and deploys a AWS Lambda application
from the machine learning application specified.
To do so, Seneca launches a docker container that mirrors the
AWS Lambda execution environment, checks and installs
the machine learning application and any libraries it requires,
and compresses the application and uploads it to S3 (avoiding
the AWS Lambda handler size restriction of 10MB).
Seneca constructs an AWS Lambda handler from a template
that, when executed, will download and uncompress the application,
download the dataset and split it into a training and testing set,
and construct, test, and evaluate a model using the application
and a set of hyperparameter values passed in by Seneca as arguments.
Users can specify the train/test split that should be used by Seneca; the
default is 80\%/20\% for classification tasks.
The handler returns a testing score. 
Upon completion of this process, the container deploys the handler
to AWS Lambda using the
AWS Command line Interface~\cite{ref:awscli}.

@@

The AWS Lambda pricing model is determined by the execution duration 
and memory. The cost of a function instance is referred to as 
\texttt{compute charge}, and is calculated as the amount of 
allocated memory multiplied by the
billed duration (execution time rounded up to the 
nearest 100ms)~\cite{ref:pricing}.
%https://aws.amazon.com/lambda/pricing/
To ensure that we keep the cost of Seneca as low as possible, we investigate
the impact of this pricing model on application execution and use
our findings to optimize cost.

Currently, allocated memory for a Lambda function can be set
between 128MB and 3008MB using increments of 64MB.
AWS documentation~\cite{ref:lambdalimits} states that Lambda 
allocates CPU to functions in way that is proportional to allocated memory size,
in the same way as is done for general purpose Amazon EC2 instance types.

@@

To verify that assertion, we conduct an experiment in which
we increase of CPU power and memory for a compute-bound 
AWS Lambda function (a microbenchmark that performs 3-D matrix multiplication~\cite{ref:matrix}).
We configure function instances to use the 46 possible allocated 
memory increments, invoke them, and record the billed duration and memory
use of each.
Figure~\ref{fig:memory} shows the relationship between allocated memory (x-axis) and reciprocal of billed duration (y-axis). 
Figure ~\ref{fig:compute_charge} shows the relationship between memory 
size (x-axis) and compute charge (y-axis). 
We observe that for this simple benchmark,
the CPU power plateaus after 1600 MB. 
Correspondingly, the compute charge declines from 128 MB to 1600 MB 
and then increases linearly.

These findings show that CPU does not proportionally increase with
an increase in allocated memory.  We use this relationship within
Seneca to optimize its cost (compute charge) via an extension
that enables it to automatically identify the appropriate
setting for allocated memory for each application.
However, instead of exhaustively testing all 46 possible 
memory configurations, which might be costly,  
Seneca employs the heuristic outlined in
Algorithm~\ref{algo:optimizer}.

The Seneca optimizer first configures and invokes the function using 
a user-defined payload.  From this run, Seneca obtains the memory 
used by function (reported by AWS Cloudwatch), 
which it uses as its starting point.
Seneca then defines two double-end queues 
(deque) of length N, to store 
allocated memory and compute charge data of different
invocations. While the current 
allocated memory is less than or equal to 3008 MB, 
the optimizer continues reconfigures and invokes the function 
using the next increment for memory allocation.  It 
calculates the compute charge for each invocation 
using current allocated memory and billed duration.

We employ two exit conditions.  The first is when the 
compute charge monotonically increases across the length of deque. 
The second is when the increase in slope is greater than a threshold. 
Once the optimizer finds that both conditions hold, 
it pops the left-most value from deque and configures 
the function to use that value for allocated memory for all future invocations.
After extensive experimentation, we find that 
N=5 and a slope threshold of 1 work well in most cases.
These values can be changed by users of the system however.
In addition, this optimization can be turned on or off via a command line
flag when starting Seneca.

@@

For parallel function invocation, Seneca integrates 
Celery~\cite{ref:celery}. Celery is an asynchronous task queue 
that uses distributed message passing. Celery workers are processes 
that take tasks from the queue, execute the tasks with the arguments specified, 
and store the result that is returned 
in a database (we use Redis~\cite{ref:redis} in our prototype).

Based on the configuration file, Seneca creates a list of 
payloads (function arguments) that contains values of 
hyperparameters.  The complete list contains all combinations of the
specified parameter
settings.  Seneca places the list on the queue and celery 
workers invoke the Lambda handler of the application, passing in the
payload (hyperparameter values) to the handler to use for model construction.  
Upon function
termination, the work records the evaluation score (and serialized model)
in the database with the hyperparameter configuration from the payload.
When the queue is drained and all workers have completed, Seneca
extracts and reports the best score, configuration, and model from the database.
Users can then evaluate the prediction power of the models (using Seneca if desired) 
for other datasets (to amortize the time/cost of Seneca) without retraining.

>>>>

To facilitate model search and selection using the serverless architecture, 
we have developed Seneca, 
a framework for tuning the hyperparameters of machine learning applications 
in AWS Lambda. 
The Seneca pipeline consists of packaging, deployment, 
function optimization, and hyperparameter tuning. Figure~\ref{fig:seneca} 
shows the architecture of Seneca.  In the the upper-right-front, we
show the three inputs that Seneca expects from its users: a hyperparameter
configuration file, a dataset URL, and the path to 
the machine learning application.
The configuration file
specifies the range of values for each hyperparameter that the 
application expects.  Seneca uses this configuration to construct
the hyperparameter search space.  The dataset URL refers to a
valid dataset stored in AWS S3.

Seneca automatically builds and deploys a AWS Lambda application
from the machine learning application specified.
To do so, Seneca launches a docker container that mirrors the
AWS Lambda execution environment, checks and installs
the machine learning application and any libraries it requires,
and compresses the application and uploads it to S3 (avoiding
the AWS Lambda handler size restriction of 10MB).
Seneca constructs an AWS Lambda handler from a template
that, when executed, will download and uncompress the application,
download the dataset and split it into a training and testing set,
and construct, test, and evaluate a model using the application
and a set of hyperparameter values passed in by Seneca as arguments.
Users can specify the train/test split that should be used by Seneca; the
default is 80\%/20\% for classification tasks.
The handler returns a testing score. 
Upon completion of this process, the container deploys the handler
to AWS Lambda using the
AWS Command line Interface\footnote{\url{https://aws.amazon.com/cli/}} 
and the developers credentials.

@@

The AWS Lambda pricing model is determined by the execution duration 
and memory of each invoked function. The cost of a function instance is referred to as 
the \texttt{compute charge}, which is the allocated memory 
multiplied by the
billed duration (execution time rounded up to the 
nearest 100ms)~\footnote{\url{https://aws.amazon.com/lambda/pricing/}}.
%https://aws.amazon.com/lambda/pricing/
To ensure that we keep the cost of Seneca as low as possible, we investigate
the impact of this pricing model on application execution and use
our findings to optimize cost.

Currently, allocated memory for a Lambda function can be set
from 128MB to 3008MB in increments of 64MB.
AWS documentation~\footnote{\url{https://docs.aws.amazon.com/lambda/latest/dg/resource-model.html}} 
states that Lambda 
allocates CPU in a way that is proportional to allocated memory size,
as is done for general purpose AWS EC2 instance types.

@@

To evaluate the impact of memory and CPU allocation on application cost,
we analyze a 3-D matrix multiple serverless benchmark~\cite{ref:matrix} using AWS Lambda.
We configure function instances to use the 46 possible allocated 
memory increments, invoke them, and record the billed duration and memory used by each.
Figure~\ref{fig:memory} shows the relationship between allocated memory 
(x-axis) and reciprocal of billed duration (y-axis). 
Figure~\ref{fig:compute_charge} shows the relationship between memory 
size (x-axis) and compute charge (y-axis). 
We observe that for this benchmark,
the CPU power plateaus after 1600 MB. 
Correspondingly, the compute charge declines from 128 MB to 1600 MB 
and then increases linearly.

These findings show that CPU does not increase proportionally with
an increase in allocated memory.  We use this relationship within
Seneca to optimize its cost (compute charge) via an extension
that enables it to automatically identify the appropriate
setting for allocated memory for each application.
However, instead of exhaustively testing all 46 possible 
memory configurations, which might be costly,  
Seneca employs the heuristic outlined in
Algorithm~\ref{algo:optimizer}.

The Seneca optimizer first configures and invokes the function using 
a user-defined payload.  From this run, Seneca obtains the memory 
used by function (reported by AWS Cloudwatch), 
which it uses as its starting point.
Seneca then defines two double-ended queues 
(deque) of length N, to store 
allocated memory and compute charge data of different
invocations. While the current 
allocated memory is less than or equal to 3008 MB, 
the optimizer reconfigures and invokes the function 
using the next increment for memory allocation.  It 
calculates the compute charge for each invocation 
using current allocated memory and billed duration.

We employ two exit conditions.  The first is when the 
compute charge monotonically increases across the deque. 
The second is when the increase in slope is greater than a threshold. 
Once the optimizer finds that both conditions hold, 
it pops the left-most value from deque and configures 
the function to use that value for allocated memory for all future invocations.
After extensive experimentation, we find that 
N=5 and a slope threshold of 1 work well in most cases.
These values can be changed by users of the system however.
In addition, this optimization can be turned on or off via a command line
argument to Seneca.

@@

For parallel function invocation, Seneca integrates 
Celery~\cite{ref:celery}. Celery is an asynchronous task queue 
that uses distributed message passing. Celery workers are processes 
that take tasks from the queue, execute the tasks with the arguments specified, 
and store the result that is returned 
in a database (we use Redis~\footnote{\url{https://redis.io/}} in our prototype).

Based on the configuration file, Seneca creates a list of 
payloads (function arguments) with
hyperparameter values.  
The complete list contains all combinations of the specified parameter
settings.  Seneca places the list on the queue and celery 
workers invoke the Lambda handler of the application, passing in the
payload (hyperparameter values) to the handler to use for model construction.  
Upon function
termination, the worker records the evaluation score (and serialized model)
in the database with the hyperparameter configuration from the payload.
When the queue is drained and all workers have completed, Seneca
extracts and reports the best score, configuration, and model from the database.
Users can then evaluate the prediction power of the models (using Seneca if desired) 
for other datasets (to amortize the time/cost of Seneca) without retraining.

### 2019-02-25 abstract.tex
chandras pass

The goal of our work is to simplify and expedite the 
construction and evaluation of machine learning models 
using autoscaled cloud computing systems and services.
To enable this, we develop an open source system, called Seneca, that leverages
the serverless programming model and its implementation in Amazon Web Services
(AWS) Lambda.  
Seneca takes a machine learning application, dataset, and a list of 
possible hyperparameter options.  It automatically constructs an AWS Lambda
handler that ingresses and splits the dataset into training
and testing portions, and constructs, tests, and evaluates (i.e. scores) a machine
learning model for a given set of hyperparameter values.  Seneca orchestrates
this execution in parallel for all possible combinations of the hyperparameters specified.
It then returns the configuration (or model) that results in the best score 
to the user.

We present the design and implementation of Seneca and introduce an extension to the
system that automatically optimizes memory use by the functions.  
Our empirical evaluation using
multiple machine learning applications for regression and classification (using
the models for prediction and not explanatory value), shows that Seneca is able to quickly
identify the best performing model,
for the datasets and algorithms that we study. 
Moreover, our memory optimization reduces the cost of using
Seneca by 10-30\% for the applications studied.

>>>>

The goal of our work is to simplify and expedite the 
construction and evaluation of machine learning models 
using autoscaled cloud computing systems and services.
To enable this, we develop an open source system, called Seneca, that leverages
the serverless programming model and its implementation in Amazon Web Services
(AWS) Lambda.  
Seneca takes a machine learning application, dataset, and a list of 
possible hyperparameter options.  It automatically constructs an AWS Lambda
handler that ingresses and splits the dataset into training
and testing subsets, and constructs, tests, and evaluates (i.e. scores) a machine
learning model for a given set of hyperparameter values.  Seneca concurrently invokes
functions for all combinations of the hyperparameters specified.
It then returns the configuration (or model) that results in the best score 
to the user.

We present the design and implementation of Seneca and introduce an extension to the
system that automatically optimizes memory use by the functions.  
Our empirical evaluation using multiple predictive machine learning applications 
for regression and classification shows that Seneca is able to quickly
identify the best performing model for the programs and datasets that we consider.
Moreover, its memory optimization reduces the cost of using Seneca 
by 10-30\% for the applications studied.

### 2019-02-25 intro.tex
chandras pass

The scale and elasticity of cloud computing systems have 
fueled remarkable innovation and unprecedented commercial 
investment.  Cloud users ``rent'' virtualized resources (while sharing
the underlying physical resources) on a pay-per-use basis
in exchange for availability guarantees specified via service level
agreements (SLAs). Uniquely, cloud systems can be configured 
to add and remove resources and services,
automatically and on-demand, based on load 
or as required by executing applications.

To date however, cloud use has been limited to large-scale 
implementations of enterprise services, such as
object storage, databases, queuing systems, and web application servers.
The reason is that it is very
challenging, even for expert users, to configure complex
distributed systems for application use, 
and to leverage the elasticity (auto-scaling) that
clouds offer. To address this challenge, cloud providers 
have started to offer cloud programming and execution environments
under the moniker of \textit{serverless} 
computing~\cite{ref:jonas2017occupy, ref:onesteptwostep, ref:peeking}.  Serverless
systems automatically configure, manage, and scale applications
to significantly simplify and broaden participation (by less expert
users) in the use of cloud systems.
%xxx: http://shivaram.org/publications/pywren-socc17.pdf
%yyy: http://cidrdb.org/cidr2019/papers/p119-hellerstein-cidr19.pdf
%zzz: L. Wang, M. Li, Y. Zhang, T. Ristenpart, and M. Swift. “Peek- ing Behind the Curtains of Serverless Platforms”. In: USENIX ATC. Boston, MA: USENIX Association, 2018

Using the serverless model, applications developers upload 
arbitrary computations in high level languages
as stateless functions to these cloud-hosted services, along with a
specification conditions under which each
function should be triggered.  Functions are invoked (triggered)
automatically by the cloud in response to external events or updates to other cloud services
(e.g. storage, queues, notification services, among others). They
communicate, persist, and access data only 
via their inputs or shared, remote storage.  
As a result, serverless applications are inherently elastic and can 
implement highly concurrent and parallel tasks.
In public clouds, users pay a small fee for the resources their 
functions use during execution, resulting in very low cost cloud use.
Although now available from all public cloud providers and as open 
source for private cloud systems, 
AWS Lambda~\cite{ref:awslambdadg} was the first and is now the 
most popular and most advanced serverless public cloud service 
available today.
%awslambda: https://docs.aws.amazon.com/lambda/latest/dg/lambda-dg.pdf

In this work, we investigate the efficacy of using AWS Lambda
for tuning machine learning applications.
To date, Lambda has not be heavily used for training and evaluating
machine learning models because of a concern that 
doing so will result in high overhead (i.e. be costly) because
of the stateless nature of serverless functions~\cite{ref:onesteptwostep}.
At the same time, identifying the ``best'' configuration for advanced
machine learning models is challenging given the large number of configuration
options (i.e. hyperparameters) typical for models today.
Hyperparameters govern the learning process of machine learning applications.
Given that parameter sweeps are embarrassingly parallel, we believe
that such tuning is a good fit for the serverless model.
To investigate this potential, its overhead, and to simplify the 
use of Lambda for training, testing, and evaluation machine learning models, 
we design and develop a new system and toolset called \textit{Seneca}.

Specifically, Seneca implements, packages, and deploys 
machine learning applications as stateless functions to AWS Lambda.
It then orchestrates exhaustive evaluation of specified hyperparameter settings
to identify the best performing model (for a given dataset) by
comparing the error and accuracy across models.  We consider
prediction accuracy (as opposed to explanatory power) as the
scoring metric (mean squared error for regression 
and accuracy percent for classification), to avoid overfitting.
Users present Seneca with their application, a range of values for 
each hyperparameter (or the default can be used), and a representative dataset.
Seneca produces, tests, and evaluates models for all combinations 
of hyperparameters and returns to the user
the set of parameters (or the model itself) that produces
the best cross-validation score (e.g. lowest squared error or highest
accuracy) for the dataset. Users can employ this model for other datasets
(with Seneca if desired) without retraining the model to amortize the cost
of Seneca further.

We deploy Seneca on AWS Lambda and evaluate its tuning performance, cost,
and memory use for six machine learning applications and datasets. We 
find that Seneca is effective for quickly training these
models and identifying the best performing hyperparameter setting for 
these applications. We also find 
Seneca to be very low cost and able to automatically 
identify the 
best memory configuration for each application further lowering its 
by 10-30\%.
As such, Seneca greatly simplifies model construction and comparison and 
does so with very low latency and at very low cost.
We intend to make Seneca and the applications available as open source
when/if this paper is accepted for publication.  In the sections
that follow, we overview our design and implementation of Seneca and then
present our empirical methodology and results.

>>>>

The scale and elasticity of cloud computing systems have 
fueled remarkable innovation and unprecedented commercial 
investment.  Cloud users ``rent'' virtualized resources (while sharing
the underlying physical resources) on a pay-per-use basis
in exchange for availability guarantees specified via service level
agreements (SLAs). Uniquely, cloud systems can be configured 
to add and remove (i.e. auto-scale) resources and services
automatically, based on the ``elastic'' resource requirements and service needs 
of executing applications.

To date however, clouds are used more for
enterprise services (object stores, databases, application servers, etc.)
than for elastic applications.
The reason for this is that it is challenging to configure complex
distributed systems for application use, 
and to leverage the auto-scaling that
clouds offer. To address this challenge, cloud providers 
have started to offer programming and execution environments
that preclude the need for server configuration,
under the \textit{serverless} moniker~\cite{ref:jonas2017occupy,ref:onesteptwostep,ref:peeking}.  
Serverless platforms automatically configure, manage, and scale applications
to significantly simplify cloud use.
%and broaden participation (by less expert
%users) in the use of cloud systems.
%xxx: http://shivaram.org/publications/pywren-socc17.pdf
%yyy: http://cidrdb.org/cidr2019/papers/p119-hellerstein-cidr19.pdf
%zzz: L. Wang, M. Li, Y. Zhang, T. Ristenpart, and M. Swift. “Peek- ing Behind the Curtains of Serverless Platforms”. In: USENIX ATC. Boston, MA: USENIX Association, 2018

Using the serverless model, application developers upload 
arbitrary computations in high level languages
as stateless functions to cloud-hosted, serverless platforms.
Functions are invoked (i.e. triggered)
automatically by the cloud in response to updates to other cloud services
(e.g. storage, queues, notification services, and API gateways, among others), which 
the developer configures. Serverless functions
communicate, persist, and access data only 
through their inputs or via shared, storage services.  
As a result, serverless applications are inherently elastic and can 
implement highly concurrent and parallel tasks.
In public clouds, users pay a small fee for the resources their 
functions use during execution, resulting in very low cost cloud use.
Although now available from all public cloud providers and as open 
source for private cloud systems, 
Amazon Web Services (AWS) Lambda\footnote{\url{https://docs.aws.amazon.com/lambda/latest/dg/lambda-dg.pdf}} %~\cite{ref:awslambdadg} 
was the first and is the most widely used
serverless public cloud platform.
%awslambda: https://docs.aws.amazon.com/lambda/latest/dg/lambda-dg.pdf

In this work, we investigate the efficacy of using AWS Lambda
for tuning machine learning applications.
To date, Lambda is not widely used for training and evaluating
machine learning models because of a concern that 
doing so will result in high overhead (i.e. be costly) because
of the stateless nature of serverless functions~\cite{ref:onesteptwostep}.
At the same time, identifying the ``best'' configuration for advanced
machine learning models is challenging given the large number of configuration
options (i.e. hyperparameters) typical for models today.
Hyperparameters govern the learning process of machine learning applications.
Given that parameter sweeps are embarrassingly parallel, we believe
that such tuning is a good fit for the serverless model.
To investigate this potential, its overhead, and to simplify the 
use of Lambda for training, testing, and evaluation of machine learning models, 
we design and develop a new system and toolset called \textit{Seneca}.

Seneca implements, packages, and deploys 
machine learning applications as stateless functions to AWS Lambda.
It then orchestrates exhaustive evaluation of specified hyperparameter settings
to identify the best performing model (for a given dataset) by
comparing error and accuracy across models.  We consider
prediction accuracy (as opposed to explanatory power) as the
scoring metric (mean squared error for regression 
and accuracy percentage for classification), to avoid overfitting.
Users present Seneca with their application, a range of values for 
each hyperparameter (or the default can be used), and a representative dataset.
Seneca produces, tests, and evaluates models for all combinations 
of hyperparameters and returns to the user
the set of parameters (or the model itself) that produces
the best cross-validation score.
Users can employ this model for other datasets
(with Seneca if desired) without retraining the model to amortize the cost
of Seneca further.

We deploy Seneca on AWS Lambda and evaluate its tuning performance, cost,
and memory use for six machine learning applications and datasets. We 
find that Seneca is fast, inexpensive, and effective for model 
construction and comparison. Seneca is also able to identify
automatically the
best memory configuration for each application, further lowering its cost
by 10-30\%.
We intend to make Seneca, its applications, and their datasets publicly available
when/if this paper is accepted for publication.  In the sections
that follow, we overview our design and implementation of Seneca and then
present our empirical methodology and results.

### 2019-02-25 results.tex
chandras pass

\begin{table}[t]
\centering
\input{tables/application-tab}
\caption{Machine learning applications used as benchmarks
to evaluate Seneca. 
%paper submission is blind (so such references must be omitted so as not to reveal our identities):
%Code base is available at project repository~\cite{ref:seneca}.
\label{tab:bmarks}}
\vspace{-0.2in}
\end{table}

@@

\begin{table}[t]
\centering
\scriptsize
\input{tables/hparams-xgboost-tab}
\caption{The hyperparameters that Seneca considers for XGBoost. 
The default value and tuning options are listed. 
\label{tab:xgboost_para}}
%\vspace{-0.2in}
\end{table}

\begin{table}[t]
\centering
\scriptsize
\input{tables/hparams-svc-tab}
\caption{The hyperparameters that Seneca considers for SVC. 
The default value and tuning options are listed. 
\label{tab:svc_para}}
%\vspace{-0.2in}
\end{table}

\begin{table}[t]
\centering
\scriptsize
\input{tables/hparams-nn-tab}
\caption{The hyperparameters that Seneca considers for NN.
The default value and tuning options are listed. 
\label{tab:nn_para}}
\vspace{-0.2in}
\end{table}

@@

In the results that follow, we evaluate \textit{default} parameterizations (that come with 
the application or that are defined by the application developer) for each application.  
The default parameters and tuning options for Prophet are listed in the Table~\ref{tab:prophet_para}. For every cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and n is the number of data points. Then the application returns the average MSE of all cross validation. Based on the model trained by default parameter setting, this average MSE metric is 0.284.

Multi-Regression is a regression application 
from an IoT project~\cite{iot-cpu} that was developed (and extended
from linear regression described in the citation, 
to multiple linear regression) by the authors.
The application predicts outdoor temperature from the processor 
temperature of single board computers (SBCs).  
The technique uses multiple linear regression models computed from time
series of processor temperature measurements,
to predict outdoor microclimate temperatures without using a temperature sensor.
%(e.g. for use in 
%precision agriculture applications such as irrigation control and frost protection).
The training dataset consists of eight input time series (one per SBC, each containing 
5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.

@@

XGBoost~\cite{ref:xgboost-web} is an open source framework for gradient boosting, which 
performs both regression and classification. We consider it a regression application and
a classification application in this evaluation.  
The hyperparameters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found at~\cite{ref:xgboostparams}.
%xgboostparams: https://xgboost.readthedocs.io/en/latest/python/python_api.html#module-xgboost.sklearn
Support vector classification (SVC)~\cite{ref:svc} is a classification algorithm 
based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
The hyperparameters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found at~\cite{ref:svcparams}.
%xvcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html
Neural network (NN)~\cite{ref:neural_network} is a machine learning framework that learns 
and make decisions from patterns in an input dataset. For this application, 
we use a feed-forward multi-layer perceptron model~\cite{ref:feedforward_nn} 
for the classification task.
The hyperparameters and their defaults that Seneca uses for Neural Network in this study are listed in Table~\ref{tab:nn_para}. A definition for each hyperparameter can be found at~\cite{ref:nnparams}.
%nn: https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPClassifier.html

For these applications (XGBoost, SVC, and NN), we use a labeled
dataset for training, testing, and evaluation from this
project~\cite{iot-cpu}. The dataset contains measurements from individual
citrus fruit (e.g. oranges, mandarins, lemons, etc.) taken by a fruit sorting
and grading device (using a large number of sensors).  The measurements (i.e.
features) include size, shape, weight, color, diameter, flatness, among other
characteristics, for each fruit.  The label indicates which field the fruit
was harvested from.  The applications train a model on a subset of the
data.  They then use this model to predict the field
from which each fruit originates. For this study we use the same random 80\%
subset of the dataset as the training dataset.  We use the remaining 20\% as the
testing dataset.

These applications compute classification accuracy score
as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
prediction class, $Y_i$ is the true class, $n$ is the number of samples, and 1(x)
is the indicator function. XGBoost also computes MSE for its regression task
on the same datasets. The dataset has been filtered to remove correlated
features (those with an absolute value of the Pearson correlation coefficient
greater than 0.8). The dataset has also been balanced by down-sampling and the resultant dataset contains
33926 rows (individual fruit) distributed evenly to 5 targets and each row has
18 features.

>>>>

\begin{table}[t]
\centering
\input{tables/application-tab}
\caption{Machine learning applications used as benchmarks
to evaluate Seneca. 
%paper submission is blind (so such references must be omitted so as not to reveal our identities):
%Code base is available at project repository~\cite{ref:seneca}.
\label{tab:bmarks}}
%\vspace{-0.2in}
\end{table}

\begin{table}[t]
\centering
%\scriptsize
\input{tables/hparams-xgboost-tab}
\caption{The hyperparameters that Seneca considers for XGBoost. 
The default value and tuning options are listed. 
\label{tab:xgboost_para}}
%\vspace{-0.2in}
\end{table}

\begin{table}[t]
\centering
%\scriptsize
\input{tables/hparams-svc-tab}
\caption{The hyperparameters that Seneca considers for SVC. 
The default value and tuning options are listed. 
\label{tab:svc_para}}
%\vspace{-0.2in}
\end{table}

\begin{table}[t]
\centering
%\scriptsize
\input{tables/hparams-nn-tab}
\caption{The hyperparameters that Seneca considers for NN.
The default value and tuning options are listed. 
\label{tab:nn_para}}
\vspace{-0.2in}
\end{table}

@@

@@

In the results that follow, we evaluate \textit{default} parameterizations (that come with 
the application or that are defined by the application developer) for each application.  
The default parameters and tuning options for Prophet are listed in the Table~\ref{tab:prophet_para}. For every cross validation, the application computes mean square error (MSE) as $\frac{1}{n}\sum_{i=1}^{n}(Y_i - \hat{Y_i})$, where $\hat{Y_i}$ is the ground truth, $Y_i$ is model prediction and n is the number of data points. Then the application returns the average MSE across cross validations. 
%Based on the model trained by default parameter setting, this average MSE metric is 0.284.

Multi-Regression is a regression application developed as part of
an Internet-of-Things (IoT) project~\cite{iot-cpu} (and extended
from linear regression described in the citation, 
to multiple linear regression by the authors of this prior work).
The application predicts outdoor temperature from the processor 
temperature of single board computers (SBCs).  
The technique uses multiple linear regression models computed from time
series of processor temperature measurements,
to predict outdoor microclimate temperatures. % without using a temperature sensor.
%(e.g. for use in 
%precision agriculture applications such as irrigation control and frost protection).
The training dataset consists of eight input time series (one per SBC, each containing 
5-minute measurements) from April 5th, 2018 to Dec. 10th, 2018.

@@

XGBoost~\cite{ref:xgboost-web} is an open source framework for gradient boosting, which 
performs both regression and classification. We consider it a regression application and
a classification application in this evaluation.  
The hyperparameters and their defaults that Seneca uses in this study are listed in Table~\ref{tab:xgboost_para}. A definition for each hyperparameter can be found in~\cite{ref:xgboostparams}.
%xgboostparams: https://xgboost.readthedocs.io/en/latest/python/python_api.html#module-xgboost.sklearn

Support vector classification (SVC)~\cite{ref:svc} is a classification algorithm 
based on support vector machine and implemented by libsvm~\cite{ref:libsvm} library.
The hyperparameters and their defaults that Seneca uses for SVC in this study are listed in Table~\ref{tab:svc_para}. A definition for each hyperparameter can be found in~\cite{ref:svcparams}.
%xvcparams: https://scikit-learn.org/stable/modules/generated/sklearn.svm.SVC.html

Neural network (NN)~\cite{ref:neural_network} is a machine learning framework that learns 
and makes decisions from patterns in an input dataset. For this application, 
we use a feed-forward multi-layer perceptron model~\cite{ref:feedforward_nn} 
for the classification task.
The hyperparameters and their defaults for NN are listed in Table~\ref{tab:nn_para}. 
A definition for each hyperparameter can be found in~\cite{ref:nnparams}.
%nn: https://scikit-learn.org/stable/modules/generated/sklearn.neural_network.MLPClassifier.html

For the classification applications (XGBoost, SVC, and NN), we use a labeled
dataset for training, testing, and evaluation from an IoT 
project~\cite{blind}. The dataset contains measurements from individual
citrus fruit (e.g. oranges, mandarins, lemons, etc.) taken by a fruit sorting
and grading device (using a large number of sensors).  The measurements (i.e.
features) include size, shape, weight, color, diameter, flatness, among other
characteristics, for each fruit.  
The dataset has been filtered to remove correlated
features (those with an absolute value of the Pearson correlation coefficient
greater than 0.8). The dataset has also been balanced by down-sampling and the resulting 
dataset contains 33926 rows (individual fruit) distributed evenly to 5 targets and each row has
18 features.  The label indicates which field the individual fruit was harvested from.  
The application trains a model on a subset (80\%) of the
data.  They then use this model to predict the field
from which each fruit originates (for the remaining 20\%).

The classification applications compute a classification accuracy score
as $\frac{1}{n}\sum_{i=1}^{n}1(Y_i = \hat{Y_i})$, where $Y_i$ is the
prediction class, $Y_i$ is the true class, $n$ is the number of samples, and 1(x)
is the indicator function. XGBoost also computes MSE for its regression task
on the same datasets.
